Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
new figures

To evaluate the performance of these models, we establish a gold standard for comparison.
In our evaluation of each dataset, a held out set of 1000 documents and labels were
reserved for evaluation and predictive performance was evaluated against the observed
labeling. Specifically, ancestors of observed nodes were ignored, observed nodes 
were considered positive and unobserved nodes were considered to be negative. The gold
standard defined in this way will likely lead to a slight overestimation of the number of
false positives. It is known that ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives.
However, given that the label space is often large (as in our examples) these potentially
erroneous false positives should not skew results significantly.

>>>>

To evaluate the performance of these models, we establish a gold standard for comparison.
In our evaluation of each dataset, a held out set of 1000 documents and labels were
reserved for evaluation and predictive performance was evaluated against the observed
labeling. Specifically, ancestors of observed nodes were ignored, observed nodes 
were considered positive and unobserved nodes were considered to be negative. This method of 
defining positive and negative labels was chosen to be as fair as possible to all models
being compared.  In particular, since the sLDA model does not enforce the hierarchical
constraints, the models can be compared on a more equal footing by focusing on the observed labels
as positives. The gold standard defined in this way will likely lead to a slight overestimation of the number of
false positives. It is known that ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives.
However, given that the label space is often large (as in our examples) it is a moderate assumption that
erroneous false positives should not skew results significantly.
